Polka-dotted Stars: Mapping the Surface of HAT-P-11

### 2023-08-15 src/tex/ms.tex
intro

>>>>

The planet-hosting star HAT-P-11 has been extensively studied for its star spots. HAT-P-11 is orbited by a Neptune-sized exoplanet, HAT-P-11b, 
which was discovered in 2008 via the transit method \citep{Bakos2010,Deming2011}. The transiting nature of HAT-P-11b has allowed for detailed 
characterization of the star spot activity on HAT-P-11, as star spots that are occulted during the planet's transit cause detectable brightening in 
the transit light curve \citep{Morris2017}.
